Descriptive, not injunctive, social norms caused increases in mask wearing during the COVID-19 pandemic

### 2023-03-30 manuscript.Rmd
change data availability statement

# Open Practices Statement

All data and code to reproduce the statistical analyses in this manuscript are publicly available on GitHub: https://github.com/ScottClaessens/covidMaskWearing This study was not preregistered.

>>>>

# Data Availability Statement

All data and code to reproduce the statistical analyses in this manuscript are publicly available on GitHub: https://github.com/ScottClaessens/covidMaskWearing

### 2023-03-30 manuscript.tex
suppress supps page and line numbering
change data availability statement

\hypertarget{open-practices-statement}{%
\section{Open Practices Statement}\label{open-practices-statement}}

All data and code to reproduce the statistical analyses in this manuscript are publicly available on GitHub: \url{https://github.com/ScottClaessens/covidMaskWearing} This study was not preregistered.

@@

\renewcommand{\appendixname}{\textbf{Supplementary Material}}
\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{S\arabic{table}} \setcounter{equation}{0}

>>>>

\hypertarget{data-availability-statement}{%
\section{Data Availability Statement}\label{data-availability-statement}}

All data and code to reproduce the statistical analyses in this manuscript are publicly available on GitHub: \url{https://github.com/ScottClaessens/covidMaskWearing}

@@

\renewcommand{\appendixname}{\textbf{Supplementary Material}}
\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{S\arabic{table}} \setcounter{equation}{0}
\pagenumbering{gobble}
\nolinenumbers
